### 2016-09-15 Chapters/SolvationAndCorrelation.tex
More polish + add a couple of TODOs

The second order energy correction will be formed including first order
amplitudes and polarization, while using zeroth order multipliers:
\begin{equation}\label{eq:second-order-G}
  \begin{aligned}
  G^{[2]} &=
  \braket{\mathrm{HF} | \commutator{\Phi}{T^{[1]}} | \mathrm{HF}}
  + \frac{1}{2}{}^t\p^{[1]}\V\p^{[1]} +
  {}^t\p^{[1]}\s_{\mathrm{N}}^{[1]}(\tamp{}^{[1]}, \tbar{}^{[0]}) \\
  &= E^{[2]}
  +
  \frac{1}{2}{}^t\p^{[1]}\V\p^{[1]}
  +
  {}^t\p^{[1]}\braket{\mathrm{HF} | \commutator{\s}{T^{[1]}_1} | \mathrm{HF}}
  = E^{[2]}
  \end{aligned}
\end{equation}
The polarization terms were eliminated by virtue of Eq.
\eqref{eq:1st-order-pol}. Formally, $G^{[2]}$ has the same expression as
\emph{in vacuo}. However, the first-order singles amplitudes are nonzero
and are determined by the quantum/classical polarizable coupling term.

@@

@@

>>>>

The second order energy correction will be formed including first order
amplitudes and polarization, while using zeroth order multipliers:
\begin{equation}\label{eq:second-order-G}
  \begin{aligned}
  G^{[2]} &=
  \braket{\mathrm{HF} | \commutator{\Phi}{T^{[1]}} | \mathrm{HF}}
  + \frac{1}{2}{}^t\p^{[1]}\V\p^{[1]} +
  {}^t\p^{[1]}\s_{\mathrm{N}}^{[1]}(\tamp{}^{[1]}, \tbar{}^{[0]}) \\
  &= E^{[2]}
  +
  \frac{1}{2}{}^t\p^{[1]}\V\p^{[1]}
  +
  {}^t\p^{[1]}\braket{\mathrm{HF} | \commutator{\s}{T^{[1]}_1} | \mathrm{HF}}
  = E^{[2]}
  \end{aligned}
\end{equation}
The polarization terms were eliminated by virtue of Eq.
\eqref{eq:1st-order-pol}. Formally, $G^{[2]}$ has the same expression as
\emph{in vacuo}. However, the first-order singles amplitudes are nonzero
and are determined by the quantum/classical polarizable coupling term.
\todo[inline]{This expression is consistent with electrostatics and
perturbation theory. Comment how this wouldn't be the case if one uses
the nonlinear Hamiltonian formulation for the quantum/classical coupling.}

@@

\todo[inline]{Develop MBPT for the approximate Lagrangians}

@@

\todo[inline]{Give the CC2, CC3 and the (T) corrections (symmetric and
asymmetric) equations.}
